`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-01-02 inst/manuscript/manuscript.rmd
'clean = FALSE' dows NOT apear to work from the yaml header but must be called from the console: rmarkdown::render('inst/manuscript/manuscript.rmd', 'bookdown::pdf_document2', clean = FALSE);

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: no
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
clean: no
csl: biomed-central.csl
bibliography: flippant.bib
---

>>>>

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: no
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
csl: biomed-central.csl
bibliography: flippant.bib
---
